---
title: "Variabilité de la marche"
author: "Fabien Leboeuf"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Richard SEM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message=FALSE
)

devtools::load_all()
#library(pyrCGM2)
windowsFonts(Times=windowsFont("TT Times New Roman"))
```


```{r}
filename <- dirname(getwd()) %+% "/data/gaitReliability/Reliability_CGM24_10Sub_3Op_2Ses.xlsx"
kinematicTable0 = read_excel(filename ,col_names = TRUE,.name_repair = "minimal")



```


```{r}

# homegeize tabe with same
kinematicTable =  kinematicTable0%>%
  homogeniseCycles(c("Id","Operator","Session"))%>% 
  constructOverallEvents(c("Id","Operator","Session"))%>%
  defineComparisonfactor(c("Operator","Session"))
```

## Standard error of measurement


```{r sem}

nParticipant = 10
nAssessor = 3

# data preparation
gkt = kinematicTable  %>%
  pivot_longer(starts_with("Frame"),names_to = "Frames", values_to = "Value")%>%
  rename(Participant = Id, 
         Assessor = Operator)

# computation
sadf = ComputeSessionAverage(gkt)
semAss = Sem_byAssessor(sadf)
semAll = Sem_allAssessors(sadf)
ba = betweenAssessors(sadf)
tes = withinAssessorReport(semAss,nAssessor,nParticipant)

```
**withinassessor report**
```{r}
tes = withinAssessorReport(semAss,nAssessor,nParticipant)
tes$Label = as.factor(tes$Label)
tes$Label = factor( tes$Label,levels( tes$Label)[c(5,3,4,1,2)]) #  reorder as Pevis,hip, knee, angles


knitr::kable(arrange(filter(tes,Assessor=="OP01"),Label),
             digits = 2,
             caption = "Within Assessor #1 report")

knitr::kable(arrange(filter(tes,Assessor=="OP02"),Label),
             digits = 2,
             caption = "Within Assessor #2 report")

knitr::kable(arrange(filter(tes,Assessor=="OP03"),Label),
             digits = 2,
             caption = "Within Assessor #2 report")


```

```{r, fig.width=12}
ggplot(data= tes, aes(x= Label, y=SemAvg, fill= Axis))+geom_bar(stat="identity",position = "dodge")+facet_grid(.~Assessor)+ggtitle("Within Assessor")+
  geom_errorbar(aes(ymin=SemAvg, ymax=IC_up), width=.2,
                position=position_dodge(.9))+
  geom_text(aes(label=round(IC_up,2),y=IC_up), vjust=0, color="black",
            position = position_dodge(0.9), size=3.5)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+ylim(0,10)
```



**between assessor report**
```{r}
comparisonBA = betweenAssessorsReport(ba)
comparisonBA$Label = as.factor(comparisonBA$Label)
comparisonBA$Label = factor( comparisonBA$Label,levels( comparisonBA$Label)[c(5,3,4,1,2)]) #  reorder as Pevis,hip, knee, angles


knitr::kable(arrange(filter(comparisonBA,Assessor=="OP01"),Label),
             digits = 2,
             caption = "Within Assessor #1 report")

knitr::kable(arrange(filter(comparisonBA,Assessor=="OP02"),Label),
             digits = 2,
             caption = "Within Assessor #2 report")

knitr::kable(arrange(filter(comparisonBA,Assessor=="OP03"),Label),
             digits = 2,
             caption = "Within Assessor #2 report")


# knitr::kable(arrange(comparisonBA,Label),
#            digits = 2,
#            caption = "Between Assessor report")


```

```{r, fig.width=12}
ggplot(data= comparisonBA, aes(x= Label, y=AbsoluteDifference, fill= Axis))+geom_bar(stat="identity",position = "dodge")+facet_grid(.~Assessor)+
  ggtitle("Between Assessor ( Absolute difference)")+
  geom_text(aes(label=round(AbsoluteDifference,2)), vjust=1, color="black",
            position = position_dodge(0.9), size=3.5)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
